\documentclass[a4paper]{paper}
\usepackage[utf8]{inputenc}

\title{ARC42}
\author{Braam van Heerden}
\date{September 2018}

\begin{document}

\maketitle

\newpage\section{Introduction and Goals}
Describes the relevant requirements and the driving forces that software architects and development team must consider. These include
\begin{itemize}
    \item underlying business goals, essential features and functional requirements for the system
    \item quality goals for the architecture
    \item relevant stakeholders and their expectations
\end{itemize}
\subsection{Requirements Overview}
\textbf{Contents}\newline
Short description of the functional requirements, driving forces, extract (or abstract) of requirements. Link to (hopefully existing) requirements documents (with version number and information where to find it).\newline\newline
\textbf{Motivation}\newline
From the point of view of the end users a system is created or modified to improve support of a business activity and/or improve the quality.\newline\newline
\textbf{Form}\newline
Short textual description, probably in tabular use-case format. If requirements documents exist this overview should refer to these documents.
Keep these excerpts as short as possible. Balance readability of this document with potential redundancy w.r.t to requirements documents.
\subsection{Quality Goals}
\subsection{Stakeholders}
\newpage\section{Architecture Constraints}
\newpage\section{System Scope and Context}
\subsection{Business Context}
\subsection{Technical Context}
\newpage\section{Solution Strategy}
\newpage\section{Building Block View}
\subsection{Whitebox Overall System}
\subsection{level 2}
\subsection{level 3}
\section{Runtime View}
\subsection{Runtime Scenario 1}
\subsection{Runtime Scenario 2}
\subsection{Runtime Scenario 3}
\newpage\section{Deployment View}
\subsection{Infrastructure Level 1}
\subsection{Infrastructure Level 2}
\subsubsection{Infrastructure Element 1}
\subsubsection{Infrastructure Element 2}
\newpage\section{Cross-cutting Concepts}
\subsection{Concept 1}
\subsection{Concept 2}
\newpage\section{Design Decisions}
\newpage\section{Quality Requirements}
\subsection{Quality Tree}
\subsection{Quality Scenarios}
\newpage\section{Risks and Technical Debts}
\newpage\section{Glossary}
\end{document}
